\documentclass{article}
\usepackage{amsfonts, amsmath, amssymb}
\usepackage{graphicx} % Required for inserting images
\usepackage{hanging}
\usepackage{hyperref}

\title{Immigration}
\author{Charlene R. Ramos}
\date{May 2024}

\begin{document}

\maketitle

\section{Abstract} 
How should scarce legal service resources be allocated to refugees and asylum seekers? 

\section{Introduction}

\begin{hangparas}{.25in}{1}

\textbf{Congressional Budget Office.} \textit{The Demographic Outlook: 2024 to 2054}. January 2024, accessed May 11, 2024 at \href{https://tinyurl.com/37zcmst9}{link}.

\textbf{Greiner, D. James and Cassandra Wolos Pattanayak. }“Randomized Evaluation in Legal Assistance: What Difference Does Representation (Offer and Actual Use) Make?” \textit{Yale Law Journal} 121, no. 8 (June 2012): 2118–2214, accessed May 11, 2024 at \href{https://tinyurl.com/m3e27cbm}{link}.

\textbf{Greiner, D. James.} “What We Know and Need to Know about Outreach and Intake by Legal Services Providers.” \textit{South Carolina Law Review} 67, no. 2 (Winter 2016): 287–294, accessed May 11, 2024 at \href{https://scholarcommons.sc.edu/sclr/vol67/iss2/8/}{link}.

\textbf{Transactional Records Access Clearinghouse.} “Too Few Immigration Attorneys: Average Representation Rates Fall from 65\% to 30\%.” January 24, 2024, accessed May 11, 2024 at \href{https://trac.syr.edu/reports/736/}{link}.

\textbf{U.S. Department of State.} “Laws \& Regulations.” Accessed May 13, 2024 at \href{https://travel.state.gov/content/travel/en/legal/visa-law0/laws-regulations.html}{link}.

\end{hangparas}

\section{Literature Review}

\begin{hangparas}{.25in}{1}

\textbf{Björkegren, Daniel, Joshua E. Blumenstock, and Samsun Knight.} 
“(Machine) Learning What Policies Value.” June 3, 2022, accessed May 11, 2024 at \href{https://arxiv.org/abs/2206.00727}{link}.

\textbf{Dunn, Matt, Hale Şirin, Levent Sagun, and Daniel Chen.} “Early Predictability of Asylum Court Decisions.” Proceedings of the 16th edition of the International Conference on Artificial Intelligence and Law, June 2017, at pp. 233–236, accessed May 11, 2024 at \href{https://tinyurl.com/mpjt4sb5}{link}.

\textbf{Haushofer, Johannes, Paul Niehaus, Carlos Paramo, Edward Miguel, and Michael W. Walker.} “Targeting Impact versus Deprivation.” National Bureau of Economic Research, Working Paper Series, June 2022, accessed May 11, 2024 at \href{https://www.nber.org/papers/w30138}{link}.

\end{hangparas}

\section{Data}

\begin{hangparas}{.25in}{1}

\textbf{IPUMS}. \textit{IPUMS CPS}. 2023, accessed May 11, 2024 at \href{https://doi.org/10.18128/D030.V11.0}{link}.

\textbf{Transactional Records Access Clearinghouse.} “About the Data on Asylum.” November 16, 2022, accessed May 11, 2024 at \href{https://tinyurl.com/yn9s2vbx}{link}. 

\textbf{Transactional Records Access Clearinghouse.} "Asylum Decisions through April 2024." Accessed May 11, 2024 at \href{https://tinyurl.com/5n8pe5rn}{link}. 

\textbf{Transactional Records Access Clearinghouse.} "Asylum Filings through November 2022." Accessed May 11, 2024 at \href{https://tinyurl.com/3dkay4yr}{link}. 

\textbf{Transactional Records Access Clearinghouse.} "Judge-by-Judge Asylum Decisions in Immigration Courts FY 2018-2023," October 19, 2023, accessed May 11, 2024 at \href{https://tinyurl.com/3zanp3xj}{link}. 

\textbf{Transactional Records Access Clearinghouse.} "Immigration Court Asylum Backlog through December 2023." Accessed May 11, 2024 at \href{https://tinyurl.com/3pw26wcj}{link}. 

\textbf{U.S. Department of Homeland Security, U.S. Customs and Border Protection.} “CBP Public Data Portal.” Accessed May 11, 2024 at \href{https://www.cbp.gov/newsroom/stats/cbp-public-data-portal}{link}. 

\textbf{U.S. Department of Homeland Security, U.S. Customs and Border Protection.} "Nationwide Encounters." Accessed May 11, 2024 at \href{https://www.cbp.gov/document/stats/nationwide-encounters}{link}. 

\textbf{U.S Department of State, Bureau of Consular Affairs.} \textit{Visa Statistics}. Accessed May 13, 2024 at \href{https://travel.state.gov/content/travel/en/legal/visa-law0/visa-statistics.html}{link}. 

\textbf{U.S Department of State, Bureau of Consular Affairs.} \textit{Immigrant Visa Statistics}. Accessed May 13, 2024 at \href{https://travel.state.gov/content/travel/en/legal/visa-law0/visa-statistics/immigrant-visa-statistics.html}{link}. 

\end{hangparas}

\section{Methodology}

\[ \sum_{h} \sum_{t=0}^{\bar t} W(Y_{h,t}(T_h)) = 
\sum_{h} \sum_{t=0}^{\bar t} W(Y_{h,t}^0 + T_h \cdot \Delta_{h,t}))
\]

\[ \hat{Y_t^0(X_h)} \text{ of } \mathbb{E} [Y_t^0 \rvert X_h ,t ] \]

\[ \hat{\Delta X_h} \text{ of } \mathbb{E} [Y_t^1 - Y_t^0 \rvert X_h ,t ] \]  

\section{Results}

\section{Discussion}

\begin{hangparas}{.25in}{1}

\textbf{Hainmueller, Jens, Duncan Lawrence, Linna Martén, Bernard Black, Lucila Figueroa, Michael Hotard, Tomás R. Jiménez, Fernando Mendoza, Maria I. Rodriguez, Jonas J. Swartz, and David D. Laitin.} “Protecting Unauthorized Immigrant Mothers Improves their Children’s Mental Health.” \textit{Science} 357, no. 6355 (August 31, 2017): 1041–1044, accessed May 11, 2024 at \href{https://www.science.org/doi/10.1126/science.aan5893}{link}.

\textbf{Hunt, Will. }“Reshoring Chipmaking Capacity Requires High-Skilled Foreign Talent.” Center for Security and Emerging Technology, February 2022, accessed May 11, 2024 at \href{https://doi.org/10.51593/20210065}{link}.

\end{hangparas}

\section{Conclusion}
\section{References}

\end{document}
